Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-03 draft/draft.tex
progress

Bla bla...

>>>>

Consider a set of $N=n+1$ teams labeled by $\{0,1,...,n\}$ to be rated and ranked.
For this aim, assume that some set of pairwise comparison scores $\psi_{ij}=-\psi_{ji}$ is provided for each $ij$ of different labels $i$ and $j$.
Informally, the score $\psi_{ij}$ should be positive if the pairwise comparison indicates that team $i$ should be rated higher than team $j$ and it should be non-positive otherwise.
One way to obtain rating scores somehow consistent with the pairwise comparisons scores, consist in finding ratings $w_i$ for $i=0,1,..,n$ such that minimize the sum of squared differences
$$
\sum_{ij:i<j} |\psi_{ij}-(w_i-w_j)|^2.
$$
